H0LiCOW: correlation between black hole mass and host galaxy luminosity.

### 2020-02-29 manuscript/manuscript.tex
Update before pull from overleaf

We adopt a class of consistent recipes as introduced in~\citet{Ding2020} to estimate the \mbh\ of our sample. \ding{Do we want to include the detailed information such as recipe and the other things here?}

\begin{table}
\centering
%\begin{threeparttable}
\caption{Summary of lensed \mbh\ estimates.}\label{data_set}
\resizebox{8.5cm}{!}{
     \begin{tabular}{ccccc}
        \hline
Object ID & Line(s) used & FWHM & log($L_\lambda$) & $\log$\mbh \\
& & (\kms) & (${\rm erg~s^{-1}}$) & (M$_{\odot}$) \\ \hline
HE0435 & \Mgii & 4930 & 45.14 & 8.54 \\
RXJ1131 & \Mgii/\Hb & 5630/4545 & 44.29/44.02 & 8.26/8.23 \\
WFI2033 & \Mgii & 3960 & 45.19 & 8.38 \\
SDSS1206 & \Mgii & 5632 & 45.61 & 8.88 \\
HE1104 & \Civ & 6004 & 46.18 & 9.03 \\
SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 \\
HE0047 & \Mgii & 4145 & 45.59 & 8.60 \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
      \small
      \item Note: $-$ The masses
\end{tablenotes}  
%\end{threeparttable}
\end{table}

@@

\subsubsection{RXJ1131}

@@

\subsection{Stellar mass estimates}
For those ones have multi-bands, we attempt to infer the color of the host in the image plane.

How do we infer the color? All the available bands? Which is dominating the scatter?

\section{Black Hole mass estimates}
We use viral method to estimate the mass of the black hole. The board-line adopted. We aim to adopt the self-consistent to recalibrate the \mbh~of our sample. 
[] The recipes. [] The board lines and the resulting BH mass and listed in the table. []The summarizing table.

\section{Results}
%estimate the black hole mass.

%scaling relation and compare to the Ding+20

%\ding{Do we consider the Selection effect? We only select 8 sample? Maybe we only over plot them together and see if the results are self-consistent?}

@@

>>>>

To assure the validity of the comparison, we adopt a class of self-consistent recipes as introduced in~\citet{Ding2020} to estimate the \mbh\ of our sample. For the overall systems, we adopt the following virial formalism:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
%
with a\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
b\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
%
Having achieved a consistent cross-calibration, we adopt the board line information from the literature to estimate the \mbh. The information are presented in Table~\ref{mbh}. The uncertainty of the \mbh\ are expected as $0.4$~dex.

\begin{table}
\centering
%\begin{threeparttable}
\caption{Summary of lensed \mbh\ estimates.}\label{mbh}
\resizebox{8.5cm}{!}{
     \begin{tabular}{ccccc}
        \hline
Object ID & Line(s) used & FWHM & log($L_\lambda$) & $\log$\mbh \\
& & (\kms) & (${\rm erg~s^{-1}}$) & (M$_{\odot}$) \\ \hline
HE0435 & \Mgii & 4930 & 45.14 & 8.54 \\
RXJ1131 & \Mgii/\Hb & 5630/4545 & 44.29/44.02 & 8.26/8.23 \\
WFI2033 & \Mgii & 3960 & 45.19 & 8.38 \\
SDSS1206 & \Mgii & 5632 & 45.61 & 8.88 \\
HE1104 & \Civ & 6004 & 46.18 & 9.03 \\
SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 \\
HE0047 & \Mgii & 4145 & 45.59 & 8.60 \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
      \small
      \item Note: $-$ The reference for the board line information. For SDSS1206, we follow Birrer2018 and consider the magnification effect to correct the L.
\end{tablenotes}  
%\end{threeparttable}
\end{table}

@@

\subsubsection{RXJ1131}
The RXJ1131 is the other system that has been studied in \citet{Ding2017b}. The host galaxy is lensed to a extended arc with a feature of bulge $+$ disk clearly appeared, we consider them both in the fitting.

We compare to the previous reconstructions. The bulge are consistent, however, our inferred disk are brighter.

@@

\subsection{Stellar mass estimates}
[] Color inference for the first three cases to decide their stellar template.

[] For the other systems, we follow Ding to assume their age based on their redshift.

The uncertainty of the \mstar\ are considered as 0.2 dex, and as studied in~\citet{Ding2017a}, we expect that the uncertainty of the \mbh\ dominate the error budget.

%\section{Black Hole mass estimates}
%We use viral method to estimate the mass of the black hole. The board-line adopted. We aim to adopt the self-consistent to recalibrate the \mbh~of our sample. 
%[] The recipes. [] The board lines and the resulting BH mass and listed in the table. []The summarizing table.

\section{Results}
Derive the the inference of our sample, we over plot our measurements on top of the measurements by \citet{Ding2020}, shown in Figure. The result demonstrate an excellent consistency. and the result support the evolution.

@@

Look at the future? JWST and TDCOSMO will extend the sample size.
